A Loop Quantm Gravity Inspired Action for the Bosonic String and Emergent Dimensions at Large Scales

### 2025-02-25 lqg-strings.tex
did some minor tweak to the solution of the gauged model and very minor stuff in discussion

from which the pulledback connection $\mc{A}_{a} = \del _{a} X^{\mu} \mc{A}_{\mu}$ is thus
\begin{equation} \label{eqn:adS-WS-connection}
	\mc{A}_{a} = \begin{bmatrix} 0 & 0 & 0 & 0 & \del _{a} X^{0} \\ 0 & 0 & 0 & 0 & \del _{a} X^{1} \\ 0 & 0 & 0 & 0 & \del _{a} X^{2} \\ 0 & 0 & 0 & 0 & \del _{a} X^{3} \\ - \del _{a} X^{0} & \del _{a} X^{1} & \del _{a} X^{2} & \del _{a} X^{3} & 0 \end{bmatrix} ,
whereby imposing conformal gauge on the induced metric $\gamma _{a b} = \del _{a} X^{\mu} \del _{b} X^{\nu} \eta _{\mu \nu} = \e ^{\varphi} \eta _{a b}$ we can separate equations for the Minkowski sector $X^{\mu}$ and for the holographic dimension $X^{r}$:

@@

Thus, the Minkowski sector behaves like regular ST for small perturbations, and for the holographic dimension we can solve using a Green's function
\begin{equation} \label{eqn:Xr-GF}
	X^{r} (x) = - 4 \mu \int \diff ^2 x' G (x ; x') \e ^{\varphi (x')} ,

@@

with the Green's function satisfying
\begin{equation} \label{eqn:Greens-function}
	(\del _{\sigma} ^2 - \del _{\tau} ^2 + 2 \mu ^2 \e ^{\varphi}) G (x ; x') = \delta ^2 (x , x') .

@@

To find this Green's function, we must fix the conformal factor to be of the form $\e ^{\varphi} = f (\tau) - g (\sigma)$, thus allowing us to separate variables in the homogeneous case of eq \eqref{eqn:Greens-function} into
\begin{equation} \label{eqn:Green-X}
	X^{\prime \prime} - 2 \mu ^2 g (\sigma) X = - \lambda X
\begin{equation} \label{eqn:Green-T}
	\ddot{T} - 2 \mu ^2 f (\tau) T = - \lambda T .
These are Schrodinger's equations for potentials given by $\mu f (\tau)$ and $\mu g (\sigma)$, as such if we assume that $f$ and $g$ are harmonic oscillator potentials $f (\tau) = \omega ^2 \tau ^2 / 2$ and $g (\sigma) = k^2 \sigma ^2 / 2$ we can find known solutions for separation constant $\lambda = 2 \mu E = \mu k (2n + 1) = \mu \omega (2n + 1)$, so by the Spectral Theorem our separated spatial and temporal Green's functions are
\begin{equation} \label{eqn:X-function}
	X (\sigma , \sigma ') = \sum _{n \geq 0} - \frac{X_{n} (\sigma) X_{n} (\sigma ')}{\mu k (2 n + 1)}
\begin{equation} \label{eqn:T-function}
	T (\tau , \tau ') = \sum _{m \geq 0} - \frac{T_{m} (\tau) T_{m} (\tau ')}{\mu \omega (2 m + 1)} ,
where $X_{n}$ and $T_{m}$ are harmonic oscillator eigenfunctions. With this, the full Green's function $G = T.X$ and the solution for $X^{r}$ are thus
\begin{equation} \label{eqn:G-function}
	G (x ; x') = \sum _{m \geq 0} \sum _{n \geq 0} \frac{T_{m} (\tau) T_{m} (\tau ')}{\mu \omega (2 m + 1)} \frac{X_{n} (\sigma) X_{n} (\sigma ')}{\mu k (2 n + 1)}
\begin{multline} \label{eqn:Xr-solution}
	X^{r} (x) = - 4 \mu \sum _{m \geq 0} \sum _{n \geq 0} \frac{T_{m} (\tau)}{\mu \omega (2 m + 1)} \frac{X_{n} (\sigma)}{\mu k (2 n + 1)} \times \\
	\times \int \diff ^2 x' T_{m} (\tau ') X_{n} (\sigma ') \left( \frac{\omega ^2 \tau ^{\prime 2}}{2} - \frac{k^2 \sigma ^{\prime 2}}{2} \right) .

@@

@@

In section \ref{sec:quantum-kg-string} we saw that our area-corrected model allows closed string spin-1 excitations, which is due to our solution not having distinct left and right sectors and the physical states not being invariant under rigid rotations of the string. Closed string excitations are usually related to the gravitational field and background spacetime itself, so what could the vector states of the closed string relate to? Well, in section \ref{sec:gauging-lt} we discussed a possible formulation of ST in terms of a Poincaré connection $\mc{A}_{\mu}$, which is an ingredient in describing the gravitational field in tetrad-connection \cite{Bodendorfer-LQG} formulation, and so this seems to be the natural candidate as to what the first level vector excitation of the closed string could be,
\begin{equation} \label{eqn:connection-string-vector-excitation}
	\mc{A}_{\mu} \sim \eta _{\mu \nu} (\Hat{a}^{\nu} _{1})^{\dagger} \ket{0} .
\end{equation}
Another candidate for what the vector excitations could relate to is the Ashtekar electric field $\widetilde{E}^{\mu} _{I}$,
\begin{equation} \label{eqn:AEF-string-vector-excitation}
	\widetilde{E}^{\mu} _{I} \sim (\Hat{a}^{\mu} _{I})^{\dagger} \ket{0} .
\end{equation}

>>>>

from which the pulledback connection is $\mc{A}_{a} = \del _{a} X^{\mu} \mc{A}_{\mu}$, whereby imposing conformal gauge on the induced metric $\gamma _{a b} = \del _{a} X^{\mu} \del _{b} X^{\nu} \eta _{\mu \nu} = \e ^{\varphi} \eta _{a b}$ we can separate equations for the Minkowski sector $X^{\mu}$ and for the holographic dimension $X^{r}$:

@@

Thus, the Minkowski sector behaves like regular ST for small perturbations, while the holographic coordinate $X^{r}$ follows a variable-mass Klein-Gordon equation with source. Now it should be clear why the choice of $\mu$ for the coupling constant, since in \eqref{eqn:simplified-holographic-EoM} it appears (together with the conformal factor) as a mass term for our perturbation. Eq \eqref{eqn:simplified-holographic-EoM} can be solved using the 1d wave equation Green's function to build a perturbation around the homogenous wave equation solution
\begin{multline} \label{eqn:holo-sol-implicit}
	X^{r} (x) = X^{r} _{0} (x) - \\ - 2 \mu \int \diff ^2 x' G (x ; x') \e ^{\varphi (x')} (2 + \mu X^{r} (x')) = \\ = X^{r} _{0} (x) + \delta X^{r} (x),
where $X^{r} _{0}$ is a solution for the homogenous wave equation
\begin{equation} \label{eqn:homo-wave-eqn}
	(\partial _{\sigma} ^{2} - \del _{\tau} ^{2}) X^{r} _{0} = 0

@@

and $G (x ; x') = \frac{1}{2} \Theta (\tau - \tau ' - |\sigma - \sigma '|)$ its Green's function
\begin{equation} \label{eqn:homo-wave-eqn-GF}
	(\partial _{\sigma} ^{2} - \del _{\tau} ^{2}) G (x ; x') = \delta ^{2} (x ; x') .

@@

From \eqref{eqn:holo-sol-implicit}, a recursion can be built, leading to a more explicit form
\begin{multline}
	X^{r} (x) = X^{r} _{0} (x) + \\ + \sum _{k \geq 1} (- 2)^{k} (\mu)^{2 k -1} \int \prod _{n = 1} ^{k} \diff ^{2} x^{(n)} G (x^{(n - 1)} ; x^{(n)}) \e ^{\varphi (x^{(n)})} \times \\ \times (2 + \mu X^{r} _{0} (x^{(k)})) ,

@@

with $x^{(0)} \equiv x$.

@@

In section \ref{sec:quantum-kg-string} we saw that our area-corrected model allows closed string spin-1 excitations, which is due to our solution not having distinct left and right sectors and the physical states not being invariant under rigid rotations of the string. Closed string excitations are usually related to the gravitational field and background spacetime itself, so what could the vector states of the closed string relate to? Well, in section \ref{sec:gauging-lt} we discussed a possible formulation of ST in terms of a Poincaré connection $\mc{A}_{\mu}$, which is an ingredient in describing the gravitational field in tetrad-connection \cite{Bodendorfer-LQG} formulation, and so this seems to be the natural candidate as to what the first level vector excitation of the closed string could be,
\begin{equation} \label{eqn:connection-string-vector-excitation}
	\mc{A}_{\mu} \sim \eta _{\mu \nu} (\Hat{a}^{\nu} _{1})^{\dagger} \ket{0} .
\end{equation}
Another candidate for what the vector excitations could relate to is the $D = 3 + 1$ Ashtekar electric field $\widetilde{E}^{a} _{i}$,
\begin{equation} \label{eqn:AEF-string-vector-excitation}
	\widetilde{E}^{a} _{i} \sim (\Hat{a}^{a} _{i})^{\dagger} \ket{0} .
\end{equation}
